Study sample characteristics in chronobiology and sleep research

### 2021-08-31 article.Rmd
Update article.Rmd
Update article.Rmd
Edit syntax.

1. Published studies on circadian and sleep physiology should be carefully examined.
1. Reporting of demographic variables should be done carefully and systematically.
2. Inclusion and diversity of different populations across the field needs to be ensured.

@@

Out of `r as.numeric(nrow(data.original))` identified and pre-screened articles, we included and extracted data from `r as.numeric(nrow(data.included))` (`r round(percent.included)`%). The distribution of years in which the articles were published is non-uniform and we included and extracted data from more recent articles (Fig. 1). In addition, the representation of journals in the final list of articles is non-uniform, not least as the included journals will not have been available for the entire data collection period (1979 and onwards).

>>>>

1. Published studies on circadian and sleep physiology should be carefully examined.
2. Reporting of demographic variables should be done carefully and systematically.
3. Inclusion and diversity of different populations across the field needs to be ensured.

@@

Out of `r as.numeric(nrow(data.original))` identified and pre-screened articles, we included and extracted data from `r as.numeric(nrow(data.included))` (`r round(percent.included)`%). The distribution of years in which the articles were published is non-uniform and we included and extracted data from more recent articles (Fig. 1). In addition, the representation of journals in the final list of articles is non-uniform, as the included journals were not all available from the start date of our data collection (1979 and onwards).
